% -*- LaTeX -*-
\documentclass[twocolumn]{article}

\usepackage{pslatex}
%\usepackage{draftcopy}
\usepackage{xspace}
\usepackage[letterpaper,twoside,hmargin={2cm,2cm},tmargin=3.5cm,bmargin=1.5cm]{geometry}
\usepackage[letterpaper,backref,colorlinks=true]{hyperref}

\newcommand{\HPCCx}{HPC~Challenge} % raw benchmark name
\newcommand{\HPCC}{\HPCCx\xspace}
\newcommand{\DGEMM}{\textsf{DGEMM}\xspace}
\newcommand{\FFT}{\textsf{FFT}\xspace}
\newcommand{\HPL}{\textsf{HPL}\xspace}
\newcommand{\PTRANS}{\textsf{PTRANS}\xspace}
\newcommand{\RANDA}{\textsf{RandomAccess}\xspace}
\newcommand{\STREAM}{\textsf{STREAM}\xspace}
\newcommand{\beff}{\textsf{b\_eff}\xspace}
\newcommand{\hpl}{\textsf{\scriptsize HPL}\xspace}
\newcommand{\randa}{\textsf{\scriptsize RandomAcccess}\xspace}
\newcommand{\fft}{\textsf{\scriptsize FFT}\xspace}

\begin{document}
\title{HPC Challenge Awards: Class 2 Specification}
\author{Jack Dongarra \and Piotr Luszczek}
\date{June 2005}
\maketitle

\tableofcontents

\section{General Guidelines}
\begin{enumerate}
\item The use of high level languages is encouraged.
\item Calls to tuned library routines could be used in the submission but
  explicit and ``elegant'' coding of all aspects of the benchmark is preferred.
\item The entire benchmark could be expressed by using a few built-in operators
  of an hypothetical programming language. However, such submissions are
  strongly discouraged as they only show operator overloading and funciton call
  syntax and say nothing about the language. In particular, how it deals with
  issues critical to HPC like expressing parallelism and hiding latency.
%  There is a Fine line between terseness and expresiveness: A\textbackslash{}b
\end{enumerate}

\section{\HPL}
\HPL~(High Performance Linpack) is an implementation of the Linpack TPP~(Toward
Peak Performance) variant of the original Linpack benchmark which measures the
floating point rate of execution for solving a linear system of equations.
\subsection{Description}
\HPL solves a linear system of equations of order $n$:
\begin{equation}
A x = b;\quad A\in\mathbf{R}^{n\times n};\; x,b\in\mathbf{R}^n
\label{eqn:axb}
\end{equation}
by first computing LU factorization with row partial pivoting of the
$n$~by~$n+1$ coefficient matrix:
\begin{equation}
P [A, b] = [[L,U], y].
\label{eqn:lu}
\end{equation}
Since the row pivoting~(represented by the permutation matrix~$P$) and
the lower triangular factor~$L$ are applied to~$b$ as the factorization
progresses, the solution~$x$ is obtained in one step by solving the upper
triangular system:
\begin{equation}
  Ux = y.
\label{eqn:ubsolve}
\end{equation}
The lower triangular matrix $L$ is left unpivoted and the array of pivots is
not returned.

\subsection{Data Size}
$A$ is~$n$ by~$n$ double precision~(in IEEE 754 sense) matrix, $b$ is
$n$-element vector. The size of the~$A$ matrix~($8n^2$ bytes) should be at
least half of the system memory.

\subsection{Initialization}
Both $A$ and $b$ should contain values produced by a reasonable pseudo-random
generator with an expected mean of zero. ``Reasonable'' in this context means
compact, fast, and producing independent and identically distributed elements.

\subsection{Timed Region}
The timed portion of the code performs steps given by equations~(\ref{eqn:lu})
and~(\ref{eqn:ubsolve}) and does not include time to generate~$A$ and~$b$.

\subsection{Duration}
Until solution to~(\ref{eqn:axb}) is obtained.

\subsection{Verification}
Correctness of the solution is ascertained by calculating the following scaled
residual:
\begin{equation}
r = \frac{\|Ax-b\|_{\infty}}{\epsilon (\|A\|_{\infty} \|x\|_{\infty}+\|b\|_{\infty}) n}
\end{equation}
where $\epsilon$ is machine precision for 64-bit floating-point values and~$n$
is the size of the problem. The solution is valid if the following holds:
\begin{equation}
  r < 16
\end{equation}

\subsection{Performance}
The operation count for the factorization phase
is~$\frac{2}{3}n^3-\frac{1}{2}n^2$ and~$2n^2$ for the solve phase thus if the
time to solution is~$t_S$ the formula for performance~(in Gflop/s) is:
\begin{equation}
  p_{\hpl}=\frac{\frac{2}{3}n^3+\frac{3}{2}n^2}{t_S}10^{-9}.
\end{equation}

\subsection{Alternative Implementations}
If an alternative algorithm is chosen it should be able to deal with zeros on
the diagonal~(some sort of pivoting needs to be used) and the precision of the
calculations needs to be preserved.

\section{\RANDA}
\subsection{Description}
Let $T[\cdot]$ be a table of size~$2^n$. \\
Let $\{a_i\}$ be a stream of 64-bit integers of length~$N_U=2^{n+2}$ generated by
the primitive polynomial over~GF(2)\footnote{Galois Field of order 2 -- The
  elements of GF(2) can be represented using the integers 0 and 1, i.e., binary
  operands.}: \\ $x^2+x+1$. \\
For each~$a_i$, set
\begin{equation}
  T[a_i\langle 63,64-n\rangle] \leftarrow T[a_i\langle 63,64-n\rangle]\oplus a_i
\label{eqn:raupdate}
\end{equation}
where:
\begin{itemize}
\item $\oplus$ denotes addition in~GF(2) i.e. "exclusive or"~(XOR)
\item $a_i\langle l,k\rangle$ denotes the sequence of bits within~$a_i$, e.g.
  $\langle 63, 64-n\rangle$ are the highest~$n$ bits.
\end{itemize}

\subsection{Data Size}
The parameter~$m(=2^n)$ is defined such that: \\
$m$ is the largest power of~$2$ that is less than or equal to half of the
system memory.  Since the elements of the main table are 64-bit quantities, the
table occupies~$8m$ bytes of memory.

\subsection{Initialization}
Table elements are set such that:
\begin{equation}
  \forall_{0\le i< 2^n} T[i]\equiv i
\label{eqn:raset}
\end{equation}

\subsection{Timed Region}
The timed region consists of computation~(\ref{eqn:raupdate}).
The initialization~(\ref{eqn:raset}) is not timed.

\subsection{Duration}
Ideally, $2^{n+2}$ updates should be performed to the main
table~($N_U=2^{n+2}$). However, the computation can be prematurely stopped
after~$25\%$ of the time of the~\HPL run (but not shorter than~$1$ minute). Thus:
\begin{equation}
  N_U \le 2^{n+2}
\end{equation}

\subsection{Verification}
The update defined by~(\ref{eqn:raupdate}) should be repeated by an
alternative method that is safe~(does not generate errors resulting from, for
example, race conditions in memory updates). If the benchmarked update was
correct, the table should return to its initial state defined
by~(\ref{eqn:raset}). However, $1\%$ of entries may have incorrect values,
i.e. given a function:
\begin{equation}
  f(i) = \left\{\begin{array}{ll}0 & \textrm{if } T[i]=i \\ 1 & \textrm{otherwise} \end{array}\right.
\end{equation}
the following should hold:
\begin{equation}
  \sum_{i=0}^{N_U}f(i) \le 10^{-2}N_U
\end{equation}

\subsection{Performance}
Let~$t_{\randa}$ be the time it took to finish the timed portion of the
test~(including~$N_U$ updates) then peroformance~(in GUPS: Giga Updates Per
Second) is defined as:
\begin{equation}
  p_{\randa} = \frac{N_U}{t_{\randa}} 10^{-9}.
\end{equation}

\subsection{Alternative Implementations}
Constraints on the look-ahead and storage before processing on distributed
memory multi-processor systems is limited to~$1024$ per process~(or
processing element). The pseudo-random number generator that generates
sequence~$\{a_i\}$ has to be used.

\section{Global EP-\STREAM{}-Triad}
\subsection{Description}
EP-\STREAM{}-Triad is a simple benchmark program that measures sustainable
memory bandwidth~(in Gbyte/s) and the corresponding computation rate for
a simple vector kernel operation that scales and adds two vectors:
\begin{equation}
a\;\leftarrow b+\alpha\;c
\label{eqn:striad}
\end{equation}
where:
\[a, b, c\in\mathbf{R}^m; \quad \alpha\in\mathbf{R}.\]

The computation is peformed simultaneously on each computing element on its
local data set.

\subsection{Data Size}
$a$, $b$, and~$c$ are $m$-element double precision vectors. The combined size
of the vectors~($24m$ bytes) should be at least quarter of the system memory.

\subsection{Initialization}
Vectors $b$ and~$c$ should contain values produced by a reasonable
pseudo-random number generator.

\subsection{Timed Region}
The timed portion of the code should perform operation given
by~(\ref{eqn:striad}) at least~$10$ times.

\subsection{Duration}
The kernel operation should be repeated at least~$10$ times.

\subsection{Verification}
The norm of the difference between reference and computed vectors is used to
verify the result: $\|a-\hat{a}\|$. The reference vector~$\hat{a}$ is obtained
by an alternative implementation.

\subsection{Performance}
The benchmark measures Gbyte/s and the number of items transferred is $3m$. The
minimum time~$t_{\min}$ is taken of all the repetitions of the kernel
operation. Performance is thus defined as:
\begin{equation}
  p_{\textrm{\scriptsize{}EP-\STREAM{}-Triad}} = 24\frac{m}{t_{\min}}10^{-9}
\end{equation}

\subsection{Alternative Implementations}

\section{Global \FFT}

\subsection{Description}
\FFT measures the floating point rate of execution of double precision
complex one-dimensional Discrete Fourier Transform (DFT) of size~$m$:
\begin{equation}
Z_k\leftarrow\sum_j^m z_j e^{-2\pi i\frac{jk}{m}}; \quad 1 \le k \le m
\label{eqn:ffft}
\end{equation}
where:
\[z, Z\in\mathbf{C}^m.\]

\subsection{Data Size}
$Z$ and~$z$ are $m$-element double precision complex vectors. The combined size
of the vectors~($32m$ bytes) should be at least quarter of the system memory.
The size~$m$ of the vectors can be implementation-specific, e.g. be an integral
power of~$2$.

\subsection{Initialization}
Vector $z$ should contain values produced by a reasonable pseudo-random number
generator. The real and imaginary parts of~$z$ should be generated
independently. The layout of vectors~$z$ and~$Z$ should not be scrambled either
before or after the computation.

\subsection{Timed Region}
The computation implied by~(\ref{eqn:ffft}) is timed together with the portion
of code that unscrambles~(if necessary) the resulting vector data. Timing for
computation and unscrambling can be given separately for informational
purposes but the combined time is used for calculating performance.

\subsection{Duration}
Until the transform defined by~(\ref{eqn:ffft}) is obtained.

\subsection{Verification}
Verification is done by acertainig the following bound on the residual:
\begin{equation}
\frac{\|z-\hat{z}\|_{\infty}}{\epsilon\,\ln m} < 16
\end{equation}
where $\hat{z}$ is the result of applying a reference implementation of the
inverse transform to the outcome of the benchmarked code~(in infinite-precision
arithmetic the residual should be zero):
\begin{equation}
\hat{z}_k\leftarrow\sum_j^m Z_j e^{2\pi i\frac{jk}{m}}; \quad 1 \le k \le m
\end{equation}

\subsection{Performance}
The operation count is taken to be~$5m\log_2 m$ for the calculation of the
computational rate~(in Gflop/s) in time~$t$:
\begin{equation}
  p_{\fft}=5\frac{m\log_2 m}{t}10^{-9}
\end{equation}

\subsection{Alternative Implementations}
The reference implementation splits the algorithm into computational and
communication portions which do not overlap. Valid submsissions may choose other
methods that take advantage of language and architectural features.

The number of processors may be implementation-specific, e.g. be an integral
power of~$2$.

\end{document}

\section{}
\subsection{Description}
\subsection{Data Size}
\subsection{Initialization}
\subsection{Timed Region}
\subsection{Duration}
\subsection{Verification}
\subsection{Performance}
\subsection{Alternative Implementations}

I think we need to say somewhere that a call to a library routine or A\b is
not the kind of elegant solution we are looking for.
Jack

Ps by the way it's not Global STREAM triad. It EP STREAM Triad on the
system, and its derived.

**********************************************************************
Jack Dongarra; Innovative Computing Laboratory; Computer Science Dept;
1122 Volunteer Blvd; University of Tennessee; Knoxville TN, 37996-3450
+1-865-974-8295; dongarra@cs.utk.edu; http://www.cs.utk.edu/~dongarra/

-----Original Message-----
From: Jeremy Kepner [mailto:kepner@ll.mit.edu] 
Sent: Monday, June 20, 2005 3:57 PM
To: Piotr Luszczek
Cc: dongarra@cs.utk.edu; Jeremy Kepner
Subject: Re: HPC Challenge Competition Announced

Piotr/Jack,
  I told Cleve on the phone that the 64 bit twiddling
was important.  More importantly,
we need a short mathematical description of the big
four that gives folks a recipe for a legal implementation
for Class 2 (these are different than a legal implementation
for Class 1).

My guess would be something like:

(1) Global HPL

Create a random (centered at zero) double precision NxN
matrix matrix that takes 1/4 to 1/2 of total system memory.

Create a random (centered at zero) double precision 1xN
vector.

Start your timer

Perform the LU factorization of the matrix using guassian
elimination with partial pivoting.

Solve the linear system.

Stop your timer.

Validate by checking various norms.

Report the performance using: list HPL performance formula.


(2) Global STREAM triad

Create three double precision vectors A, B and C of length N  such that
the combined total memory takes 1/4 to 1/2 of total system memory.

Initialize B and C to random values.

Pick a value for a scalar constant q.

Start your timer

Perform the following operation at least 10 times.

   A = q*B + C

Stop your timer.

Compute the performance using the formula

  Memory Bandwidth = N * (12 bytes) / time


(3) Global FFT

Create a random complex double precision vector of size N such that the
total memory takes 1/4 to 1/2 of total system memory.

Initialize your FFT (i.e. compute twiddle tables).

Start your timer.

Perform a 1D complex-to-complex FFT.

Stop your timer.

Perform an inverse 1D complex-to-complex FFT.

Compute the max absolute difference between
the initial input and the ouput of the inverse FFT,
should be less than 1.e-9.

Report performance using:

  Flops = 5*N*log2(N) / time

(4) RandomAccess (see David Koester's slides).


Pick a value for a scalar constant q.

Start your timer

Perform the following operation at least 10 times.

   A = q*B + C

Stop your timer.


Compute the performance using ...








Regards.  -Jeremy

On Mon, Jun 20, 2005 at 02:05:25PM -0400, Piotr Luszczek wrote:

>> Jack and Jeremy,
>> 
>> please correct me if I'm wrong but I think that "64-bit fiddling"
>> for RandomAccess is crucial. It's by "mission partner" request.
>> 
>> Piotr
>> 
>> Jack Dongarra wrote:
>
>>> > Cleve,
>>> > We are still trying to sort out the productivity (class 2) part of the
>>> > award. I would agree what you have is elegant but how fast is it? What

size

>>> > problem are you planning to solve? How readable is the code? The Matlab

FFT

>>> > example hides the complexity in a library. In some sense we are more
>>> > interested in how the language solves this type of problem rather than

how

>>> > it calls library routines. In the end it's subjective with 8 judges.
>>> > 
>>> > For the class 1 part you have to run the program as is, at least for the
>>> > base run. So there should be no confusion there.
>>> > 
>>> > As I said we are still sorting this out and your comments are welcomed.
>>> > Jack
>>> > 
>>> > **********************************************************************
>>> > Jack Dongarra; Innovative Computing Laboratory; Computer Science Dept;
>>> > 1122 Volunteer Blvd; University of Tennessee; Knoxville TN, 37996-3450
>>> > +1-865-974-8295; dongarra@cs.utk.edu; http://www.cs.utk.edu/~dongarra/
>>> > 
>>> > -----Original Message-----
>>> > From: Cleve Moler [mailto:Cleve.Moler@mathworks.com] 
>>> > Sent: Monday, June 20, 2005 9:50 AM
>>> > To: Jeremy Kepner; dongarra@cs.utk.edu
>>> > Subject: FW: HPC Challenge Competition Announced
>>> > 
>>> > Hi, guys --
>>> > 
>>> > I am thinking of participating in the "Productivity" portion of the HPC
>>> > Challenge Award Competition, using MATLAB.  But I don't know what level

of

>>> > "implementation" you are thinking of.
>>> > 
>>> > For example, take the 3-D FFT.  If you got to
>>> >    http://icl.cs.utk.edu/hpcc/
>>> > and click on FFTE, you are taken directly to
>>> >    http://www.ffte.jp/
>>> > where you can download a compressed zip file with a mixture of Fortran

and C

>>> > code.  It seems that HPCC benchmark is to run this code on your new
>>> > supercomputer.  I guess that may be productive, but certainly not

elegant.

>>> > 
>>> > For the FFT, at the top level, in MATLAB, we have
>>> > 
>>> >       n = some integer, probably a power of 2
>>> >       X = drandn(n,n,n);
>>> >       tic
>>> >       fft3(X);
>>> >       toc
>>> > 
>>> > You gotta admit that's elegant and productive.   Even the next level

down is

>>> > pretty nice:
>>> > 
>>> >       function X = fft3(X)
>>> >       X = fft(X,[],1);
>>> >       X = fft(X,[],2);
>>> >       X = permute(X,[3 2 1]);
>>> >       X = fft(X,[],1);
>>> >       X = permute(X,[3 2 1]);
>>> > 
>>> > Would that, along with some timings, be an acceptable entry for the FFT
>>> > portion of the competition?  What timings?  What machine?  How many
>>> > processors?
>>> > 
>>> > Likewise, for HPL.  Is the challenge to run the code from the HPL

website

>>> > with some souped-up BLAS, or is it to solve a large linear system.
>>> > 
>>> >       tic
>>> >       A\b
>>> >       toc
>>> > 
>>> > In the Random Access benchmark, do you want us to do exactly the same

64-bit

>>> > bit fiddling?
>>> > 
>>> > In other words, we need to know more about the ground rules for this
>>> > competition.
>>> > 
>>> > Thanks.
>>> > 
>>> >   -- Cleve
>>> > 
>>> > 
>>> > 
>>> > -----Original Message-----
>>> > From: HPCwire [mailto:hpcmore@news.hpcwire.com] 
>>> > Sent: Friday, June 03, 2005 12:48 AM
>>> > To: Cleve Moler
>>> > Subject: HPC Challenge Competition Announced
>>> > 
>>> > 
>>> > 
>>> > 
>>> > FEATURES
>>> > ======================================================================
>>> > [ ] M393115 ) HPC Challenge Competition
>>> > Announced.........................4.1K 
>>> > 
>>> >   The DARPA High Productivity Computing Systems (HPCS) Program and 
>>> >   HPCWire are pleased to announce the first annual HPC Challenge Award 
>>> >   Competition (<http://www.hpcchallenge.org>).
>>> >   
>>> >   The goal of the competition is to focus the HPC community's attention 
>>> >   on a broad set of HPC hardware and HPC software capabilities that are 
>>> >   necessary to effectively use HPC systems.
>>> >   
>>> >   The core of the HPC Challenge Award Competition is the HPC Challenge 
>>> >   benchmark suite developed by University of Tennessee under the DARPA 
>>> >   HPCS program with inputs from a wide range of organizations around the


>>> >   world (see <http://icl.cs.utk.edu/hpcc/>). The Competition will focus 
>>> >   on four of the most challenging benchmarks in the suite:
>>> >   
>>> >   Global HPL
>>> >   Global RandomAccess
>>> >   Global STREAM (Triad)
>>> >   Global FFT 
>>> >   There will be two classes of awards. 
>>> >   
>>> >   Class 1: Best Performance (4 awards)
>>> >   
>>> >   Best performance on the base or optimized run submitted to the HPC 
>>> >   Challenge website.  The benchmarks to be judged are: Global HPL, 
>>> >   Global RandomAccess, Global STREAM (Triad) and Global FFT. The prize 
>>> >   will be $500 plus a certificate for the best of each.
>>> >   
>>> >   Class 2: Most Productivity
>>> >   
>>> >   Most "elegant" implementation of one or more of the HPC Challenge 
>>> >   benchmarks with special emphasis being placed on: Global HPL, Global 
>>> >   RandomAccess, Global STREAM (Triad) and Global FFT. This award would 
>>> >   be weighted 50% on performance and 50% on code elegance/clarity/size.


>>> >   Both will be determined by an evaluation committee.
>>> >   
>>> >   For this award, the implementer must submit to 
>>> >   <mailto:hpcc-awards@cs.utk.edu> (by October 15th) a short description 
>>> >   of: the implementation, the performance achieved, lines-of-code, and 
>>> >   the actual source code of their implementation. The evaluation 
>>> >   committee will select a set of finalists who will be invited to give a


>>> >   short presentation at the HPC Challenge Award BOF at SC|05.   This 
>>> >   presentation will be judged by the evaluation committee to select the 
>>> >   winner. The prize will be $1500 plus a certificate for this award and 
>>> >   may be split among the "best" entries.
>>> >   
>>> >   The awards will be presented at the HPC Challenge Award BOF at SC|05 
>>> >   and the prizes are sponsored by HPCWire. 
>>> >   
>>> >   HPC Challenge Awards Evaluation Committee 
>>> >   David Bailey, LBNL NERSC
>>> >   Jack Dongarra (Co-Chair), U of Tennessee/ORNL
>>> >   
>>> >   Jeremy Kepner (Co-Chair), MIT Lincoln Lab
>>> >   David Koester, MITRE
>>> >   Bob Lucas, ISI
>>> >   Rusty Lusk, Argonne National Lab 
>>> >   
>>> >   Piotr Luszczek, U of Tennessee
>>> >   John McCalpin, IBM Austin
>>> >   Rolf Rabenseifner, HLRS, Stuttgart
>>> >   Daisuke Takahashi, U of Tsukuba 
>>> > 
>>> > 
>>> > 
>>> >  
>>> > 
>>> > [ ] P357M382451 )                LCI Workshop at OSCER
>>> >                                    June 21-24, 2005
>>> >                                       Norman, OK
>>> >                          REGISTRATION DEADLINE: MAY 20, 2005
>>> >                         http://www.linuxclustersinstitute.org/
>>> > 
>>> > [ ] P357M382452 )  OMG's Sixth Annual Workshop on Distributed Object
>>> >                      Computing for Real-time and Embedded Systems
>>> >                                    July 11-14, 2005
>>> >                                     Washington, DC
>>> >                          Presentations, panels & discussions
>>> >                              http://www.omg.org/hpc-rte/
>>> > 
>>> > [ ] P357M320047 )             Commodity Cluster Symposium
>>> >                          On the Use of Commodity Clusters for
>>> >                          Large-Scale Scientific Applications
>>> >                                    July 26-28, 2005
>>> >                                  Greenbelt, Maryland
>>> >                          CALL FOR PARTICIPATION AND ABSTRACTS
>>> >                          http://www.arl.hpc.mil/Clusters2005
>>> > 
>>> > [ ] P357M382453 )                     Security '05
>>> >                             14th USENIX Security Symposium
>>> >                                    August 1-5, 2005
>>> >                                  Baltimore, Maryland
>>> >                          http://www.usenix.org/events/sec05/
>>> > 
>>> > [ ] P357M389465 )         **"Data Mining: Levels I, II & III"
>>> >                                 September 26-30, 2005
>>> >                                 San Diego, California
>>> > 
>>> > [ ] P357M382454 )             SC|05 - Gateway to Discovery
>>> >                                  November 12-18, 2005
>>> >                                  Seattle, Washington
>>> >                           Housing Now Open to All Attendees!
>>> >                         http://sc05.supercomputing.org/travel
>>> > 
>>> > 
>>> >

______________________________________________________________________

>>> >       Full background information on all leading HPC solution providers 
>>> > 
>>> >              [ ] A517 ) Data Direct 
>>> >              [ ] A639 ) Microway 
>>> >              [ ] A341 ) NEC 
>>> >              [ ] A518 ) Cray 
>>> >              [ ] A345 ) Myricom 
>>> >              [ ] A330 ) Atipa 
>>> >              [ ] A351 ) APPRO 
>>> >              [ ] A470 ) HP 
>>> >              [ ] A342 ) Sun 
>>> >              [ ] A335 ) IBM 
>>> >              [ ] A339 ) SGI 
>>> >              [ ] A337 ) Linux Networx 
>>> >              [ ] A332 ) Etnus/TotalView 
>>> >              [ ] A373 ) Dell 
>>> >              [ ] A338 ) PathScale 
>>> >              [ ] A331 ) Intel 
>>> >              [ ] A343 ) Portland Group 
>>> > 
>>> > 
>>> >            For sponsorship information contact: promote@hpcwire.com


>>> >

______________________________________________________________________ 

>> 


